Amicable Contempt

### 2023-12-17 manuscript/manuscript.qmd
fix errant nbsps
Uncurl quotes since pandoc deals with that

Other INGOs have made similar adaptations. In 2014, for instances, Venezuela faced a deep economic recession while simultaneously cracking down on civic space and barring international aid agencies from the country. A group of Venezuelan-Americans in Florida founded El Programa de Ayuda Humanitaria para Venezuela (PAHPV) as a response to the growing humanitarian crisis.[^2] Prohibited from setting up an office in Venezuela itself, PAHPV collected medical equipment, supplies, and other donations throughout the southeastern United States. Lacking official legal status in the country, PAHPV initially partnered with domestic Venezuelan NGOs to obtain proper permits for importing goods. Later, when unable to obtain permission, PAHPV volunteers flew to Caracas carrying supplies and cash in their luggage, distributing the donations to local NGOs upon arrival. Civic space in Venezuela was closed to foreigners, but PAHPV and similar organizations still found their way in.

@@

I theorize that each party is aware that the other both threatens and supports their existence, thus creating a state of *amicable contempt*. Governments see global civil society as a strategic player in their domestic political landscape. International NGOs can help governments maintain by providing services and expertise, and by bestowing international legitimacy and reputation. At the same time, though, INGOs pose a risk to governments. Their missions and goals might conflict with the ruling regime’s—for instance, a human rights INGO might condemn a leader who relies on torture to control dissidents. To address this dilemma, governments enact regulations and restrictions that offset the costs and risks of letting INGOs operate in their country while simultaneously capturing the political, social, and other practical benefits of these organizations.

@@

Because of the costs involved in confronting and adapting to their regulatory environment, not all INGOs are able to make these adjustments, and organizations often adjust to fit regime preferences or exit the country. I theorize that an INGO’s ability to respond to government regulations is determined by two organizational factors: (1) the degree of an INGO’s programmatic and instrumental flexibility influences how it responds to gatekeeping regulations, and (2) an INGO’s commitment to its core mission, vision and values influences how it responds to program capture regulations.

@@

Similar to DeMattee’s typology, I don’t test any hypotheses or make any causal claims. Rather, I present a conceptual framework for understanding the dynamic relationship between INGOs and host governments and illustrate its mechanisms using survey data.

@@

> [c]ore funding so we can do our work and stop spending so much time on raising money to do our work. We are activists, researchers, communications experts, we don’t want to spend our lives raising money, schmoozing funding partners and writing proposals.[^38]

>>>>

Other INGOs have made similar adaptations. In 2014, for instance, Venezuela faced a deep economic recession while simultaneously cracking down on civic space and barring international aid agencies from the country. A group of Venezuelan-Americans in Florida founded El Programa de Ayuda Humanitaria para Venezuela (PAHPV) as a response to the growing humanitarian crisis.[^2] Prohibited from setting up an office in Venezuela itself, PAHPV collected medical equipment, supplies, and other donations throughout the southeastern United States. Lacking official legal status in the country, PAHPV initially partnered with domestic Venezuelan NGOs to obtain proper permits for importing goods. Later, when unable to obtain permission, PAHPV volunteers flew to Caracas carrying supplies and cash in their luggage, distributing the donations to local NGOs upon arrival. Civic space in Venezuela was closed to foreigners, but PAHPV and similar organizations still found their way in.

@@

I theorize that each party is aware that the other both threatens and supports their existence, thus creating a state of *amicable contempt*. Governments see global civil society as a strategic player in their domestic political landscape. International NGOs can help governments maintain by providing services and expertise, and by bestowing international legitimacy and reputation. At the same time, though, INGOs pose a risk to governments. Their missions and goals might conflict with the ruling regime's—for instance, a human rights INGO might condemn a leader who relies on torture to control dissidents. To address this dilemma, governments enact regulations and restrictions that offset the costs and risks of letting INGOs operate in their country while simultaneously capturing the political, social, and other practical benefits of these organizations.

@@

Because of the costs involved in confronting and adapting to their regulatory environment, not all INGOs are able to make these adjustments, and organizations often adjust to fit regime preferences or exit the country. I theorize that an INGO's ability to respond to government regulations is determined by two organizational factors: (1) the degree of an INGO's programmatic and instrumental flexibility influences how it responds to gatekeeping regulations, and (2) an INGO's commitment to its core mission, vision and values influences how it responds to program capture regulations.

@@

Similar to DeMattee's typology, I don't test any hypotheses or make any causal claims. Rather, I present a conceptual framework for understanding the dynamic relationship between INGOs and host governments and illustrate its mechanisms using survey data.

@@

> [c]ore funding so we can do our work and stop spending so much time on raising money to do our work. We are activists, researchers, communications experts, we don't want to spend our lives raising money, schmoozing funding partners and writing proposals.[^38]
